### 2017-12-07 manuscript.rmd
fixed typoes

Bracts are highly reduced zooids unique to siphonophores, but they are only present in Codonophora. Bracts are functional for protection of the delicate zooids and to help maintain neutral buoyancy [@jacobs1937beobachtungen]. Some calycophorans are able to actively exclude sulphate ions in their bracts to adjust their buoyancy along the colony [@bidigare1980role]. As with the nectosome, we cannot be sure whether the common ancestor of siphonophores had bracts or not. The common ancestor of Codonophora had only one bract subtype, which was lost in Hippopodidae, *Physophora hydrostatica*, the Clausophyidae, and in *Gymnopraia lapislazula* (none of the latter three species and clades are included in the phylogeny). Phylogenetic reconstructions are sensitive to taxon sampling, and these patterns of loss are not captured by the present sampling [**We don't have the reconstruction in supp info - do we want to add it?**].

Palpons are modified reduced gastrozooids used for digestion and circulation of the gastrovascular fluid [@mackie1987siphonophore]. We do not disinguish here between gonopalpons (palpons associated with gonodendra, without a tentacle, as in the cystonects) and palpons borne on the stem (typically with a reduced tentacle or palpacle) [@totton1965synopsis]. They were present in the common ancestor of siphonophores (Fig. 5B), retained in most species, but lost three times independently in the branches leading to *Pyrostephidae* (represented here by the genera *Bargmannia* and *Rudjakovia*), in calycophorans (with the exception of Stephanophyes [@totton1965synopsis]), and in *Marrus claudanielis*. These taxa might have found other avenues to effectively circulate nutrients across the colony.

>>>>

Bracts are highly reduced zooids unique to siphonophores, but they are only present in Codonophora (Fig. 4). Bracts are functional for protection of the delicate zooids and to help maintain neutral buoyancy [@jacobs1937beobachtungen]. Some calycophorans are able to actively exclude sulphate ions in their bracts to adjust their buoyancy along the colony [@bidigare1980role]. As with the nectosome, we cannot be sure whether the common ancestor of siphonophores had bracts or not. The common ancestor of Codonophora had only one bract subtype, which was lost in Hippopodidae, *Physophora hydrostatica*, the Clausophyidae, and in *Gymnopraia lapislazula* (none of the latter three species and clades are included in the phylogeny). Phylogenetic reconstructions are sensitive to taxon sampling, and these patterns of loss are not captured by the present sampling [**We don't have the reconstruction in supp info - do we want to add it?**].

Palpons are modified reduced gastrozooids used for digestion and circulation of the gastrovascular fluid [@mackie1987siphonophore]. We do not distinguish here between gonopalpons (palpons associated with gonodendra, without a tentacle, as in the cystonects) and palpons borne on the stem (typically with a reduced tentacle or palpacle) [@totton1965synopsis]. They were present in the common ancestor of siphonophores (Fig. 5B), retained in most species, but lost three times independently in the branches leading to *Pyrostephidae* (represented here by the genera *Bargmannia* and *Rudjakovia*), in calycophorans (with the exception of Stephanophyes [@totton1965synopsis]), and in *Marrus claudanielis*. These taxa might have found other avenues to effectively circulate nutrients across the colony.
